Effects of Reynolds Number on the Performance and Near-Wake Dynamics of a Vertical-Axis Cross-Flow Turbine

### 2015-10-11 paper.tex
Minor wording
Add references for AFT performance Re-independence; resolves #16

Blackwell et al. investigated the effects of Reynolds number on the
performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed high Reynolds
number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$.
\todo[inline]{Add reference for Bravo et al.}

@@

The Reynolds number effects on the maximum performance and 2-D near-wake
profiles of the University of New Hampshire's Reference Vertical Axis Turbine
(UNH-RVAT) were presented in \cite{Bachant2014}. In this study we set out to
analyze in greater depth the effects of scale, i.e. Reynolds number, on the
performance of the turbine, and its more detailed near-wake characteristics. We
were looking to find a threshold scale beyond which a physical model study could
reliably predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.

>>>>

Blackwell et al. investigated the effects of Reynolds number on the
performance
of a 2 m diameter Darrieus vertical-axis cross-flow wind turbine with NACA 0012
blades \cite{Blackwell1976}. By varying wind tunnel speed, the turbine was made
to operate at approximately constant blade chord Reynolds number $Re_c$ ranging
from $1 \times 10^5$ to $3 \times 10^5$. In this regime the turbine power
coefficient $C_P$ was shown to be sensitive to $Re_c$, with sensitivity
diminishing at the higher Reynolds numbers, especially for turbines of lower
solidity ($Nc/R$, where $N$ is the number of blades and $R$ is the turbine's
maximum radius). More recently, Polagye and Cavagnaro observed high Reynolds
number sensitivity for a high solidity helical cross-flow turbine
\cite{Polagye2013b}, and Bravo et al. observed power coefficient of a
straight-bladed VAWT to become Reynolds number independent at $Re_c \approx 4
\times 10^5$ \cite{Bravo2007}.

Krogstad and Adaramola observed Reynolds number independence of the performance for a 0.9 m
diameter axial-flow turbine rotor at $Re_D \approx 5 \times 10^5$ in wind tunnel
tests \cite{Krogstad2012a}. Their turbine blades had an S826 profile along their entire span, a profile chosen for its $Re$-independence. Walker et al. \cite{Walker2014} similarly chose a NACA 63-618 foil for their axial-flow turbine tests in a towing tank, which were performed at a mid span Reynolds number $Re_c = 4 \times 10^5$.

@@

The Reynolds number effects on the maximum performance and 2-D near-wake
profiles of the University of New Hampshire's Reference Vertical Axis Turbine
(UNH-RVAT) were presented in \cite{Bachant2014}. Here we set out to
analyze in greater depth the effects of scale, i.e. Reynolds number, on the
performance of the turbine, and its more detailed near-wake characteristics. We
were looking to find a threshold scale beyond which a physical model study could
reliably predict full-scale performance. We were also looking to investigate the
sensitivity as small scales, and what the implications might be for validating
the prediction capabilities of numerical models.
